---
title: "airbnbEDA"
output: html_document
date: "2024-05-24"
---

```{r}
library(tidymodels)
library(tidyverse)
library(visdat)
library(dplyr)
library(corrplot)
library(corrr)
library(visdat)
library(ranger)
library(beepr)
library(xgboost)
library(forcats)
tidymodels_prefer()
```

Read in data frame.
Convert price 
Since there are only 143 values > 1250, I will filter to where the price per night is less than 
1250 to filter out outliers. This will help the data to be more manageable and less skewed left.
(143 not a lot in the grand scheme of 19,000 points)
```{r}
airbnb <- read_csv('DATA/Airbnb Data/Cleaned_airbnb_barcelona.csv')
airbnb_big <- read_csv('DATA/Airbnb Data/barcelona_listings.csv')
airbnb$price <- as.numeric(gsub("[\\$,]", "", airbnb$price))

#set airbnb_raw to the initial data set before I make any changes
airbnb_raw <- airbnb

airbnb <- airbnb %>% filter(price < 1250)
#Get rid of amenities
airbnb <- airbnb %>% select(-c(amenities))
```

```{r}
summary(airbnb)
```

```{r}
summary(airbnb$price)
```


```{r}
# Add number_of_reviews to airbnb
airbnb <- airbnb %>%
  left_join(select(airbnb_big, id, number_of_reviews), by = "id")

View(airbnb)
```


Visualise missing data in airbnb:
- With 24% of data missing from reviews_scores_rating I will drop the variable because it is a large chunk missing.
```{r}
airbnb %>% select(review_scores_rating) %>% vis_miss()

# Most of the data is present, the only variable with problems is reviews_scores_rating
vis_miss(airbnb)

airbnb_big %>% 
  select(c(host_response_rate, host_response_rate, host_is_superhost, neighbourhood_group_cleansed,
           property_type, room_type, accommodates, bedrooms, beds, bathrooms, price, number_of_reviews,
           reviews_per_month, review_scores_rating)) %>% 
  vis_miss()

```
Factor Categorical Variables
```{r}
airbnb$neighbourhood <- factor(airbnb$neighbourhood)
airbnb$property_type <- factor(airbnb$property_type)
airbnb$room_type <- factor(airbnb$room_type)


View(airbnb)
```

Handle Missing
```{r}
# Remove review_scores_rating because too many missing
airbnb <- airbnb %>% select(-review_scores_rating)

# Remove the NA from entire data set (zipcode 3%, host_listings_count, host_is_superhost, bathrooms)
# Percentage of data set was so small that removing NA was negligible 
# Otherwise would have either imput averages or dropped the variable in terms of zipcode
airbnb <- na.omit(airbnb)

vis_miss(airbnb)
```


Histogram of response variable (price)
```{r}
#airbnb %>% filter(price>1250) %>% count()

#airbnb  %>% ggplot( aes(x= log(price)))+geom_histogram()
ggplot(airbnb, aes(x= price)) + geom_bar(fill= 'mediumorchid') +
  theme_minimal()

ggplot(airbnb, aes(x= price)) + geom_histogram(bins = 250,fill= 'mediumorchid') +
  theme_minimal() + labs(title = 'Distribution of Nightly Price')
```

Correlation Plot
```{r}
#CORR plot of the variables I will use in the recipe
airbnb %>% 
  select(-c('...1', id, host_id, beds, number_of_reviews_ltm, has_availability)) %>% 
  select_if((is.numeric)) %>% 
    drop_na() %>% 
  cor() %>% 
  corrplot()

# Positive correlations between accommodates, bathrooms, bedrooms, beds, price
# -> might want to remove either accommodates or beds from my recipe because they 
# are highly correlated, same with beds and bedrooms

# Drop beds and accommodates, keep bedrooms

# Also drop availability_X
```

```{r}
#drop variables 
airbnb <- airbnb %>% select(-c(amenities, '...1', id, host_id, review_scores_rating, availability_30,
                               availability_60, availability_90, beds, number_of_reviews_ltm))
airbnb %>% 
  select(where(is.numeric)) %>% 
    drop_na() %>% 
  cor() %>% 
  corrplot(type='lower')
```

Scatter plots
```{r}
#ggplot(airbnb, aes(x=number_of_reviews_ltm, y = price)) + geom_point()
ggplot(airbnb, aes(x=minimum_nights, y = price)) + geom_point()
ggplot(airbnb, aes(x=number_of_reviews, y = price)) + geom_point()
ggplot(airbnb, aes(x=availability_365, y = price)) + geom_point()

```
Distribution of neighborhoods
```{r}
ggplot(airbnb, aes(x= neighbourhood)) + geom_bar() +theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
table(airbnb$neighbourhood)

neighborhood_filtered <- airbnb %>% 
  group_by(neighbourhood) %>% 
  summarise(frequency = n()) %>% 
  filter(frequency > 40) %>% 
  arrange(desc(frequency))

# Neighborhood_filtered is a subset of the data with the top occuring neighborhoods
neighborhood_filtered <- airbnb %>% filter(neighbourhood %in% neighborhood_filtered$neighbourhood)
neighborhood_filtered
  
ggplot(neighborhood_filtered, aes(x= neighbourhood)) + geom_bar() + 
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

Boxplot Interactions
```{r}
ggplot(airbnb, aes(x = room_type, y = price, fill = property_type)) + geom_boxplot() + theme_minimal()
```


```{r}
ggplot(airbnb, aes(x = property_type, y = price)) + geom_boxplot() +theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))

ggplot(airbnb, aes(x = property_type)) + geom_bar() +theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))

ggplot(airbnb, aes(x = number_of_reviews_ltm, y = price)) + geom_point() +theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))

airbnb %>% filter(property_type == 'Apartment') %>% 
  ggplot(aes(x= accommodates, y = price)) + geom_point()

```
```{r}
ggplot(airbnb, aes(y = number_of_reviews, x = price, fill = host_is_superhost)) + geom_point()
```

```{r}
airbnb %>% 
  group_by(neighbourhood) %>% 
  count() %>% 
  arrange(desc(n))



airbnb2 <- airbnb %>% 
  mutate(neighbourhood = fct_lump(neighbourhood, n = 20, other_level = 'Other'))


airbnb2 %>% 
  group_by(neighbourhood) %>% 
  count() %>% 
  arrange(desc(n))
ggplot(airbnb2, aes(x = neighbourhood)) + geom_bar() +theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
```


```{r}
ggplot(airbnb, aes(x = property_type)) + geom_bar(fill = 'mediumorchid') +   theme(axis.text.x = element_text(angle = 45, hjust=1))

```

```{r}
airbnb %>% group_by(property_type) %>% count() %>% arrange(n)

# Lump levels of property_type with less than 100 observations into 'Other'
airbnb2 <- airbnb %>% 
  mutate(property_type = fct_lump(property_type, n = 9, other_level = 'Other'))

airbnb2 %>% group_by(property_type) %>% count() %>% arrange(n)
ggplot(airbnb2, aes(x = property_type)) + geom_bar(fill = 'mediumorchid') + theme(axis.text.x = element_text(angle = 45, hjust=1))

```
```{r}
airbnb %>% group_by(room_type) %>% count() %>% arrange(n)

```


